Introduction of using AWS instance to run experiments

### 2022-03-05 docs/run_experiments.Rmd
Add more normalization options

```
python hrlcm/fit_compose_lr.py --exp_name unet_k15_only_clr_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
```

@@

@@

For example:
```
python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'

@@

For example:
```
python hrlcm/evaluate.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'

>>>>

```
python hrlcm/fit_compose_lr.py --exp_name unet_all_norm_200 --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 201
```

@@

### Hyperparameter tunning
#### Network parameter

Before official running, test a bit about the largest values of `num_worker`, `train_batch_size`, `val_batch_size` that could be used. For `g5.12xlarge`, these values can be:

- `num_worker`:48 (CPU cores)
- `train_batch_size`: 32 (could be a bit bigger, but it is recommended to use $2^n$)
- `val_batch_size`: 32

#### Learning rate
Also, test the optimal learning rate and scheduler to use:

- 0.001 is a good start point.
- 0.00001 is a good end point with middle value of 0.0001.

`final_lr` for `optim.AdaBound`:

- 0.01 still works fine. The default value is robust for many cases.

#### Augmentation

- Random scale
- Random flip (always use)
- Random center rotate
- Normalization
    - Dataset based standardization
    - Image based standardization
    - Image based min-max scaler

@@

For example:
```
python hrlcm/predict.py --args_path 'results/dl/unet_all_norm_200/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_all_norm_200/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'

@@

For example:
```
python hrlcm/evaluate.py --args_path 'results/dl/unet_all_norm_200/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_all_norm_200/checkpoints/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
